---
title: "ggplot2 exercises"
output: html_document
---

## 1. Read-in a data file

Read-in cleaned_example.tsv and cleaned_example.xlsx.
Compare the results.

Recommended functions:

* read_tsv()
* read_xlsx()


```{r}
# Load the required packages
library(tidyverse)
library(readxl)

# Insert code below


```

## 2. Clean up 

Read-in the .csv files in the lac_data folder, creating a single data frame.
Create new columns that hold the information contained in the file names: [date]_[genotype]_[replicate]_unstained_aligned.csv

Recommended functions:

* list.files()
* read_csv()
* basename()
* separate_wider_delim()


```{r}
# Load the required packages
library(tidyverse)

# Insert code below


```

## 3. Analyse

Read-in cleaned_example.tsv and WT.tsv, bind them together into one data frame.
Calculate the mean, median, standard deviation and standard error across the biological replicates.

Recommended functions:

* read_tsv()
* bind_rows()
* group_by()
* summarise()
* mean()
* median()
* sd()
* n()
* sqrt()


```{r}
# Load the required packages
library(tidyverse)

# Insert code below


```