---
title: "ggplot2 exercises"
output: html_document
---

## 1. Read-in a data file

Read-in cleaned_example.tsv and cleaned_example.xlsx.
Compare the results.

Recommended functions:

* read_tsv()
* read_xlsx()


```{r}
# Load the required packages
library(tidyverse)
library(readxl)

# Insert code below
setwd("/home/leonard/Applications/R/data_wrangling/") # change to path of the folder downloaded from github to use relative paths from here on

tsv_data <- read_tsv("data/cleaned_example.tsv")
csv_data <- read_csv("data/cleaned_example.csv")
xlsx_data <- read_xlsx("data/cleaned_example.xlsx", sheet = 2)

```

## 2. Clean up 

Read-in the .csv files in the lac_data folder, creating a single data frame.
Create new columns that hold the information contained in the file names: [date]_[genotype]_[replicate]_unstained_aligned.csv

Recommended functions:

* list.files()
* read_csv()
* basename()
* separate_wider_delim()


```{r}
# Load the required packages
library(tidyverse)

# Insert code below
setwd("/home/leonard/Applications/R/data_wrangling/") # change to path of the folder downloaded from github to use relative paths from here on

lac_files <- list.files(
  path = "data/lac_data/",
  pattern = ".csv",
  full.names = TRUE
)

lac_data <- read_csv(lac_files, id = "path") |> 
  mutate("file" = basename(path)) |> 
  separate_wider_delim(
    file,
    delim = "_",
    names = c("date", "genotype", "replicate"),
    too_many = "drop"
  )

```

## 3. Analyse

Read-in cleaned_example.tsv and WT.tsv, bind them together into one data frame.
Calculate the mean, median, standard deviation and standard error across the biological replicates.

Recommended functions:

* read_tsv()
* bind_rows()
* group_by()
* summarise()
* mean()
* median()
* sd()
* n()
* sqrt()


```{r}
# Load the required packages
library(tidyverse)

# Insert code below
setwd("/home/leonard/Applications/R/data_wrangling/") # change to path of the folder downloaded from github to use relative paths from here on

zfp_data <- read_tsv("data/cleaned_example.tsv") |> 
  fill(Sample, .direction = "down") |>
  filter(Sample != "Blank") |> 
  select(
    Sample,
    Replicate,
    "Proportion" = `Weight%` # wrap non-syntactic names in backticks (``)
  ) |> 
  separate_wider_delim(
    Sample,
    names = c("Genotype", "Biorep"),
    delim = " "
  )
  
wt_data <- read_tsv("data/WT.tsv", col_types = "ccnn")

data <- zfp_data |> 
  bind_rows(wt_data)

summary_data <- data |> 
  group_by(Genotype, Biorep) |> 
  summarise(tech_mean_prop = mean(Proportion)) |> 
  group_by(Genotype) |> 
  summarise(
    mean_prop = mean(tech_mean_prop),
    median_prop = median(tech_mean_prop),
    sd_prop = sd(tech_mean_prop),
    se_prop = sd(tech_mean_prop) / sqrt(n())
  )

```